---
title: "My Data Project"
author: "-- Insert author here -- -- Insert address here --" 
date: "Wed Jun 28 2018"
output:
  html_document:
    toc: true
    theme: united
  pdf_document:
    toc: true
    highlight: zenburn
---

```{r, echo = FALSE}
## load packages
library(knitr)
library(rmarkdown)
library(ggplot2)
library(compareGroups)

## load data, plot and table
load(file.path("data/derived", "summary_small2_csv.RData"))

## set up a couple of variable for printing
N.CASES <- dim(df1)[1]
N.VARS <- dim(df1)[2]
```

# Summary Statistics

Data were cleaned and summary statistics presented here are for
`r ifelse(SUBSET, "a subset of", "")`
`r N.CASES` cases from `r N.VARS` variables.

## Summary Tables

Sometimes summaries can produce problematic output for *knitr* but
really should be OK or use the package *pandoc* etc

```{r, results='asis'}
knitr::kable(psych::describe(df1))
```

Much nicer to use some better functions. We already produced and save
this table before.

```{r, results='asis'}
export2md(table1)
```

## Summary Plots

We could make some new ones or just use the one we saved previously.

```{r, echo=FALSE}
ggpairs1
```

# Statistical Analysis

Ideally, you analyse data using *R* and simply output and discuss the
results here.

```{r, echo=FAlSE, results='asis'}
if (exists(mod1) {
  mod1 <-
    lm(bmi.21 ~ bpSys.21 + ysrExter.14 + matEducat + sex,
       data = df1)
  knitr::kable(summary(mod1)$coeff, digi = 3)
  knitr::kable(Anova(mod1))
}
```
But we can and should make the table look better

```{r}
knitr::kable(summary(mod1)$coeff, digi = 3, caption = "Regression Coefficients")
```

And perhaps produce som some residual plots

```{r, echo=FALSE}
plot(mod1)
```

```{r, echo=FALSE}
if (exists(mod1)) car::residualPlots(mod1)
```

And we could plot effects.

```{r, echo=FALSE}
  library(effects)
  plot(allEffects(mod1))
}
```

For more information about *R* markdown, please see
<http://rmarkdown.rstudio.com>.

Note that an 'echo = FALSE' parameter was added to the code chunk to
prevent printing of the R code that generated the plot. You can find
out more about options at <http://yihui.name/knitr/options/>.
